Drawing Math

### 2022-05-09 paper/Paper.tex
prog

\subsubsection*{Case 1}
Observe that the inner sum,
$
  \sum_{q = 0}^{\rationalPeriodTotal - 1}
  \exp\left(
      \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
        \sum_{\ell = 0}^{q}\mathrm{digit}(n, b, d, \ell)
  \right)
$,
is invariant for all $p$ in equitation \eqref{eq:inner-outer-split}. So then,
let the inner sum equal $C \in \Z$.  Moreover, note that 
\begin{align*}
  &\exp\left(
      pI \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
      \digSumPeriodic
    \right)\\
  =& \prod_{j \in A_d} \exp\left(-1^{\beta_{(j)}} pI \cdot \digSumPeriodic \right)
\end{align*}
and that 
\begin{equation*}
  \exp\left(-1^{\beta_{(j)}} pI \cdot \digSumPeriodic \right) = \exp\left(0\right) = 1
\end{equation*}
when $p = \frac{\totalPeriod}{\rationalPeriodTotal}$. Then, we can see that
$$
\prod_{j \in A_d} \exp\left(-1^{\beta_{(j)}} pI \cdot \digSumPeriodic \right) = 1
$$
when $p = \frac{\totalPeriod}{\rationalPeriodTotal}$.

@@

So, we have now shown that \eqref{eq:wts01} is always $0$ or $1$. In particular, we also have our first 
closure result. If, $\forall \beta \in \set{0, 1}^{|A_d|}$, $\sum_{j \in A_d} -1 ^ {\beta_{(j)}} \neq 0$,
\begin{align*}
  \sum_{i = 1}^T \combSingleTerm{d} &=  2^{-|A|} 
  \sum_{\beta \in \set{0,1}^{|A_d|}} 
      \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \sum_{q = 0}^{\rationalPeriodTotal - 1}
     \exp\left(
         \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
         \seedAngle{p \rationalPeriodTotal + q}I
       \right) \\
        &= 0
\end{align*}
for all $d \in D$.
So then, $\Delta P_{0, T} = 0$ whenever 
no degree $1$ multinomials with coefficients of $-1$ or $1$ and $|A_d|$ variables has a root of $(\digSumPeriodicNoJ^1, \digSumPeriodicNoJ^2, ..., \digSumPeriodicNoJ^{|A_d|})$.
In other words, if variables, $x_1 = \digSumPeriodicNoJ^1, x_2 = \digSumPeriodicNoJ^2, ...$, there does not exist a multinomial
of form $\pm x_1 \pm x_2 \pm ... \pm x_{|A_d|} = 0$.

>>>>

\subsubsection*{Case 1}
Observe that the inner sum,
$
  \sum_{q = 0}^{\rationalPeriodTotal - 1}
  \exp\left(
      \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
        \sum_{\ell = 0}^{q}\mathrm{digit}(n, b, d, \ell)
  \right)
$,
is invariant for all $p$ in equitation \eqref{eq:inner-outer-split}. So then,
let the inner sum equal $C_\beta \in \Z$.  Moreover, note that 
\begin{align*}
  &\exp\left(
      pI \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
      \digSumPeriodic
    \right)\\
  =& \prod_{j \in A_d} \exp\left(-1^{\beta_{(j)}} pI \cdot \digSumPeriodic \right)
\end{align*}
and that 
\begin{equation*}
  \exp\left(-1^{\beta_{(j)}} pI \cdot \digSumPeriodic \right) = \exp\left(0\right) = 1
\end{equation*}
when $p = \frac{\totalPeriod}{\rationalPeriodTotal}$. Then, we can see that
$$
\prod_{j \in A_d} \exp\left(-1^{\beta_{(j)}} pI \cdot \digSumPeriodic \right) = 1
$$
when $p = \frac{\totalPeriod}{\rationalPeriodTotal}$.

@@

So, we have now shown that \eqref{eq:wts01} is always $0$ or $1$. In particular, we also have our first 
closure result. If, $\forall \beta \in \set{0, 1}^{|A_d|}$, $\sum_{j \in A_d} -1 ^ {\beta_{(j)}} \neq 0$,
\begin{align*}
  \sum_{i = 1}^T \combSingleTerm{d} &=  2^{-|A|} 
  \sum_{\beta \in \set{0,1}^{|A_d|}} 
      \sum_{p= 0}^{\frac{\totalPeriod}{\rationalPeriodTotal} - 1} \sum_{q = 0}^{\rationalPeriodTotal - 1}
     \exp\left(
         \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
         \seedAngle{p \rationalPeriodTotal + q}I
       \right) \\
        &= 0
\end{align*}
for all $d \in D$.
So then, $\Delta P_{0, T} = 0$ whenever 
no degree $1$ multinomials with coefficients of $-1$ or $1$ and $|A_d|$ variables has a root of $(\digSumPeriodicNoJ^1, \digSumPeriodicNoJ^2, ..., \digSumPeriodicNoJ^{|A_d|})$.
In other words, if variables, $x_1 = \digSumPeriodicNoJ^1, x_2 = \digSumPeriodicNoJ^2, ...$, there does not exist a multinomial
of form 
$$
  \pm x_1 \pm x_2 \pm ... \pm x_{|A_d|} = 0.
$$

% TODO: replace this eqWTSInnerProf with like P_{}(d) or smthng...
In the case that $\exists \beta \in \set{0, 1}^{|A_d|}$ such that $\sum_{j \in A_d} -1 ^ {\beta_{(j)}} = 0$, it is still possible
for
$$
\eqWTSInnerProd = 0
$$
if $C_\beta = 0$. So, 
\begin{equation*}
  \sum_{q = 0}^{\rationalPeriodTotal - 1}
  \exp\left(
      \sum_{j \in A_d} -1 ^ {\beta_{(j)}}
        \sum_{\ell = 0}^{q}\mathrm{digit}(n, b, d, \ell)
  \right) = 0
\end{equation*}
